%==============================================================
%  CV — Radesh Govind  (single page, all targets)
%  pdflatex CV-Radesh_Govind.tex
%==============================================================
\documentclass[9.5pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scaled=0.92]{helvet}
\renewcommand\familydefault{\sfdefault}

\usepackage[
  top=0.50in, bottom=0.50in,
  left=0.65in, right=0.65in
]{geometry}

\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{tabularx}
\usepackage{parskip}
\usepackage{array}

%──────────────────────────────────────────────────────────────
%  Palette
%──────────────────────────────────────────────────────────────
\definecolor{navy}{HTML}{1C2B4A}
\definecolor{body}{HTML}{1F1F1F}
\definecolor{soft}{HTML}{6B7280}
\definecolor{rule}{HTML}{D1D5DB}
\definecolor{accent}{HTML}{2563EB}

\color{body}
\hypersetup{urlcolor=accent, colorlinks=true}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

%──────────────────────────────────────────────────────────────
%  Section heading — uppercase label + rule
%──────────────────────────────────────────────────────────────
\titleformat{\section}
  {\fontsize{10.5pt}{7.5pt}\selectfont\bfseries\color{soft}\raggedright}
  {}{0em}{\MakeUppercase}
  [\vspace{2pt}\textcolor{rule}{\rule{\linewidth}{0.4pt}}\vspace{0pt}]
\titlespacing*{\section}{0pt}{7pt}{3pt}

%──────────────────────────────────────────────────────────────
%  Lists
%──────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.1em,
  itemsep=1.2pt,
  topsep=2pt,
  parsep=0pt,
  label={\textcolor{soft}{\footnotesize--}}
}

%──────────────────────────────────────────────────────────────
%  Macros
%──────────────────────────────────────────────────────────────
\newcommand{\entry}[3]{%
  \noindent\textbf{\color{navy}#1}\hfill{\small\textcolor{soft}{#3}}\\[-2pt]
  {\small\textcolor{soft}{#2}}\par\vspace{1pt}%
}
\newcommand{\project}[2]{%
  \noindent{\textbf{\color{navy}#1}}\hfill{\small\textcolor{soft}{#2}}\par\vspace{1pt}%
}
\newcommand{\sep}{\enspace{\textcolor{rule}{|}}\enspace}

%==============================================================
\begin{document}
\pagestyle{empty}

%──────────────────────────────────────────────────────────────
%  HEADER
%──────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{23pt}{23pt}\selectfont\bfseries\color{navy} Radesh Govind - Software Engineer}\\[4pt]
  {\footnotesize\textcolor{soft}{%
    Lisbon, Portugal%
    \sep\href{mailto:radesh.govind@gmail.com}{radesh.govind@gmail.com}%
    \sep\href{tel:+351919125376}{+351 919 125 376}%
    \sep\href{https://linkedin.com/in/radesh-govind}{linkedin.com/in/radesh-govind}%
    \sep\href{https://github.com/radesh-govind}{github.com/radesh-govind}%
  }}
\end{center}

\vspace{1pt}
\noindent\textcolor{navy}{\rule{\linewidth}{0.8pt}}
\vspace{4pt}

%──────────────────────────────────────────────────────────────
%  SUMMARY
%──────────────────────────────────────────────────────────────
{\small%
Final-year BSc Computer Science Engineering student at ISEL Lisbon.
Currently building a AI-powered Multiplatform Application for \href{https://ureka.eu/innovate/#euprojects}{\textbf{U!REKA}}.
Strong in \textbf{Kotlin}, \textbf{Spring Boot}, \textbf{cloud-native architecture}, and production observability. 

Open to Backend, Cloud, and AI engineering roles from \textbf{July 2026.}%
}

\vspace{2pt}

%──────────────────────────────────────────────────────────────
%  TECHNICAL SKILLS
%──────────────────────────────────────────────────────────────
\section{Technical Skills}
{\small
\renewcommand{\arraystretch}{1.55}
\begin{tabularx}{\linewidth}{@{}
  >{\bfseries\color{navy}\raggedright\arraybackslash}m{1.3in}
  >{\raggedright\arraybackslash}X @{}}

Languages        & Kotlin, Java, TypeScript, Python, JavaScript, C \\
Backend          & Spring Boot, RESTful APIs,  AI Inference APIs, Node.js,
                   LangChain4j  \\
Data             & PostgreSQL, pgvector, MongoDB, JPA, JDBI, JDBC \\
Infra \& DevOps  & Docker, Docker Compose, CI/CD, Prometheus, Grafana, Nginx \\
Mobile           & Kotlin Multiplatform (KMP), Compose Multiplatform,
                    Jetpack Compose \\
Concepts         & Distributed Systems, Concurrency,
                    Event-Driven Architecture,\\
                   & Cloud-Native, MVVM/MVI, DDD, TDD \\
\end{tabularx}
}

%──────────────────────────────────────────────────────────────
%  PROJECTS
%──────────────────────────────────────────────────────────────
\section{Projects}

%── Project 1 ─────────────────────────────────────────────────
\project{U!REKA Play4Change \textnormal{\small\textcolor{soft}{%
  --- Multiplatform Adaptive Learning Platform ·
  BSc Final Year Project}}}{On Going}

\begin{itemize}\small

  \item \textbf{Engineered} a production-ready \textbf{RESTful} Spring Boot backend
        \textbf{persisted} with PostgreSQL and \textbf{containerized} with Docker Compose.

  \item \textbf{Built} a cost-optimised \textbf{AI inference pipeline} and on-demand
        adaptive branching with similarity-based reuse.

  \item \textbf{Instrumented} full Prometheus + Grafana \textbf{observability}.

  \item \textbf{Architected} a Kotlin Multiplatform \textbf{monorepo}
        with layered modules applying DDD and offline-first sync.

\end{itemize}

\vspace{3pt}

%── Project 2 ─────────────────────────────────────────────────
\project{Real-Time Multiplayer Android Game \textnormal{\small\textcolor{soft}{%
  --- 6-Player Concurrent Backend}}}{Academic · Grade: 20/20}

\begin{itemize}\small
  \item \textbf{Spring Boot} backend + \textbf{PostgreSQL} persistence + \textbf{Docker};
        \textbf{Server-Sent Events} for real-time game-state push (zero polling).
  \item Concurrency via Kotlin \textbf{Coroutines, Flows, and Channels};
        structured concurrency eliminating race conditions across 6 live sessions.
  \item Ktor network layer with \textbf{swappable mock/production transports}
        --- full offline testability without backend dependency.
\end{itemize}

\vspace{3pt}

%── Project 3 ─────────────────────────────────────────────────
\project{AI Interview Assistant \textnormal{\small\textcolor{soft}{%
  --- Stateful Edge Agent on Cloudflare Workers}}}{Personal Project}

\begin{itemize}\small
  \item \textbf{Cloudflare Workers} + Hono + \textbf{Workers AI inference API};
        session state migrated from KV to \textbf{Durable Objects}
        (Actor Model) to eliminate concurrent-session race conditions.
  \item Prompt metadata enrichment to sharpen \textbf{LLM inference quality}
        without increasing token cost; deployed globally at the edge.
\end{itemize}

%──────────────────────────────────────────────────────────────
%  EDUCATION
%──────────────────────────────────────────────────────────────
\section{Education}

\entry
  {ISEL --- Instituto Superior de Engenharia de Lisboa}
  {BSc Computer Science Engineering ~·~ Technical avg. 18--20/20 ~·~ Mobile project: 20/20}
  {2023 -- July 2026}

\entry
  {Cambridge English}
  {First Certificate in English (B2) ~·~ Credential C3622995}
  {2023}

%──────────────────────────────────────────────────────────────
%  LEADERSHIP
%──────────────────────────────────────────────────────────────
\section{Leadership \& Activities}

{\small\noindent%
\textbf{\color{navy}FNKP --- Federação Nacional de Karaté de Portugal}%
\hfill\textcolor{soft}{Technical Arbitration Official · National Level}\\[1pt]
\textcolor{soft}{High-stakes real-time decisions under pressure;
regulatory compliance and conflict resolution at national competitions.}}

\end{document}